---
title: "US BLS Worker Fatalities: Agriculture, Forestry, Fishing and Hunting (GP2AFH) Industry: PNW States (AK, ID, OR, and WA), 2011-2021"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# Attach packages, installing as needed
if(!requireNamespace("pacman", quietly = TRUE)) install.packages("pacman")
pacman::p_load(conflicted, here, readr, dplyr, tidyr, stringr, purrr, forcats,
               flexdashboard, ggplot2, plotly)

# Set options
options(readr.show_col_types = FALSE, readr.show_progress = FALSE)
conflicts_prefer(dplyr::filter(), .quiet = TRUE)

# Read data file
data_dir <- here("Fatality Data NW")
rds_file <- here(data_dir, 'long-bls-fatal-aff-11-21.rds')
csv_file <- here(data_dir, 'long-bls-fatal-aff-11-21.csv')
if (file.exists(rds_file)) {
  df <- readRDS(rds_file)
} else {
  df <- read_csv(csv_file)
  saveRDS(df, rds_file)
}

df <- df %>% filter(`code` == "GP2AFH")

# Find level-1 Characteristics
Char_1 <- df %>% filter(!is.na(Char_2), is.na(Char_3)) %>% pull(Char_1) %>% 
  unique()
```


```{r, include = FALSE}
# Define a function to make a generic ggplot object without any geoms
make_ggplot <- function(df, x_label, by = 'State', wrap_width = 50, 
                        color = FALSE) {
  p_levels <- df %>% pull(Characteristic) %>% unique()
  p_labels <- p_levels %>% str_wrap(width = wrap_width)
  df <- df %>% 
    mutate(Characteristic = factor(Characteristic, 
                                   levels = p_levels,
                                   labels = p_labels)) %>%
    select(State, !!x_label := Characteristic, Year, Fatalities) %>% 
    drop_na(Fatalities)
  if (color == FALSE) {
    ggplot(df, aes(x = .data[[x_label]], y = Fatalities))
  } else {
    x_var <- ifelse(by == 'State', 'Year', 'State')
    ggplot(df, aes(x = .data[[x_var]], y = Fatalities, 
                   color = .data[[x_label]], fill = .data[[x_label]]))
  }
}

# Define a function to make a generic ggplot object without any geoms 
# filtered by Char_1 == Char1
make_ggplot_1 <- function (df, Char1, Char2 = NULL, Char3 = NULL, by = 'State', 
                           wrap_width = 50, color = FALSE) {
  df <- df %>% 
    filter(Char_1 == Char1, !is.na(Char_2), is.na(Char_3)) %>% 
    select("Characteristic" = Char_2, Fatalities, State, Year)
  make_ggplot(df, Char1, by = by, wrap_width = wrap_width, color = color)
}

# Define a function to make a generic ggplot object without any geoms 
# filtered by Char_1 == Char1 and Char_2 == Char2
make_ggplot_2 <- function (df, Char1, Char2, Char3 = NULL, by = 'State', 
                           wrap_width = 50, color = FALSE) {
  df <- df %>% 
    filter(Char_1 == Char1, Char_2 == Char2, !is.na(Char_3), is.na(Char_4)) %>% 
    select("Characteristic" = Char_3, Fatalities, State, Year)
  make_ggplot(df, Char2, by = by, wrap_width = wrap_width, color = color)
}

# Define a function to make a generic ggplot object without any geoms 
# filtered by Char_1 == Char1 and Char_2 == Char2 and Char_3 == Char3
make_ggplot_3 <- function (df, Char1, Char2, Char3, by = 'State', 
                           wrap_width = 50, color = FALSE) {
  df <- df %>% 
    filter(Char_1 == Char1, Char_2 == Char2, Char_3 == Char3, 
           !is.na(Char_4), is.na(Char_5)) %>% 
    select("Characteristic" = Char_4, Fatalities, State, Year)
  make_ggplot(df, Char3, by = by, wrap_width = wrap_width, color = color)
}

# Define a function to make a box plot building upon a generic ggplot object
make_boxplot <- function(df, Char_1, Char_2 = NULL, Char_3 = NULL, by = 'State', 
                         wrap_width = 50, nrow = NULL, color = FALSE, 
                         FUN = NULL) {
  if (is.null(nrow)) nrow <- ifelse(by == "Year", 2, 1)
  if (is.null(FUN)) {
    FUN = case_when(
      is.null(Char_2) && is.null(Char_3) ~ "make_ggplot_1",
      !is.null(Char_2) && is.null(Char_3) ~ "make_ggplot_2",
      .default = "make_ggplot_3"
    )
  }
  
  arg <- list(df = df, Char1 = Char_1, Char2 = Char_2, Char3 = Char_3, by = by,
              wrap_width = wrap_width)
  do.call(FUN, arg) + geom_boxplot() + facet_wrap(by, nrow = nrow) + 
    coord_flip()
}

# Define a function to make a scatter plot building upon a generic ggplot object
make_scatterplot <- function(df, Char_1, Char_2 = NULL, Char_3 = NULL, 
                             by = 'State', wrap_width = 50, color = TRUE, 
                             nrow = NULL, FUN = NULL) {
  if (is.null(nrow)) nrow <- ifelse(by == "Year", 2, 1)
  if (is.null(FUN)) {
    FUN = case_when(
      is.null(Char_2) && is.null(Char_3) ~ "make_ggplot_1",
      !is.null(Char_2) && is.null(Char_3) ~ "make_ggplot_2",
      .default = "make_ggplot_3"
    )
  }
  
  arg <- list(df = df, Char1 = Char_1, Char2 = Char_2, Char3 = Char_3, by = by,
              wrap_width = wrap_width, color = color)
  flip <- if (by == "Year") coord_flip()
  smooth <- if (by == "State") geom_smooth(method = "lm", formula = y ~ x)
  do.call(FUN, arg) + geom_point() + 
    smooth + facet_wrap(by, nrow = nrow) + flip
}

# Define a function to make a bar plot building upon a generic ggplot object
make_barplot <- function(df, Char_1, Char_2 = NULL, Char_3 = NULL, 
                             by = 'State', wrap_width = 50, color = TRUE, 
                             nrow = NULL, FUN = NULL) {
  if (is.null(nrow)) nrow <- ifelse(by == "Year", 2, 1)
  if (is.null(FUN)) {
    FUN = case_when(
      is.null(Char_2) && is.null(Char_3) ~ "make_ggplot_1",
      !is.null(Char_2) && is.null(Char_3) ~ "make_ggplot_2",
      .default = "make_ggplot_3"
    )
  }
  
  arg <- list(df = df, Char1 = Char_1, Char2 = Char_2, Char3 = Char_3, by = by,
              wrap_width = wrap_width, color = color)
  flip <- if (by == "Year") coord_flip()
  fill_color <- ifelse(by == "Year", "State", "Year")
  do.call(FUN, arg) + geom_col() + facet_wrap(by, nrow = nrow) + flip
}

plot_bar_char <- function(df, Char, nrow = 1, wrap_width = 60) {
  ggplot(df %>% 
           filter(Characteristic %in% Char) %>% 
           mutate(Year = factor(Year)) %>%
           mutate(Characteristic = str_wrap(Characteristic, wrap_width)) %>%
           group_by(Characteristic, State, Year) %>%
           summarise(Fatalities = sum(Fatalities, na.rm = TRUE), 
                     .groups = "drop"), 
  aes(x = Year, Fatalities, fill = State)) + geom_col() + 
    facet_wrap("Characteristic", nrow = nrow)
}
```

```{r, include=FALSE}
# Top-5 Characteristics to plot at finer detail
df %>% filter(!is.na(Char_1), !is.na(Char_2), !is.na(Char_3)) %>% 
  group_by(Char_1, Char_2) %>% 
  summarise(Fatalities = sum(Fatalities, na.rm = TRUE)) %>% 
  filter(Fatalities != 0) %>% arrange(desc(Fatalities), Char_1, Char_2) %>% 
  head(5)

# Top-15 Characteristics to plot at even finer detail
df %>% filter(!is.na(Char_1), !is.na(Char_2), !is.na(Char_3), !is.na(Char_4)) %>%
group_by(Char_1, Char_2, Char_3) %>%
summarise(Fatalities = sum(Fatalities, na.rm = TRUE)) %>%
filter(Fatalities != 0) %>% arrange(desc(Fatalities), Char_1, Char_2, Char_3) %>%
head(15)

# Top-3 Level-3 Characteristics per Category
cats <- unique(df$Char_1)
top3 <- map(cats, ~ df %>% filter(Char_1 == .x, !is.na(Char_2), 
                                  !is.na(Char_3), is.na(Char_4)) %>%
              group_by(Characteristic) %>% 
              summarise(Fatalities = sum(Fatalities, na.rm = TRUE), 
                        .groups = "drop") %>% 
              arrange(desc(Fatalities)) %>% head(3) %>% 
              pull(Characteristic)) %>% setNames(cats)
```

Total
=======================================================================

Row {data-height=300}
-----------------------------------------------------------------------

```{r}
df_total <- df %>% 
  filter(Char_1 == "Total") %>%
  group_by(Year, State) %>% 
  summarize(Fatalities = sum(Fatalities, na.rm = TRUE), .groups= "drop") %>%
  filter(Fatalities != 0) %>% arrange(State, Year, Fatalities)
```

### Annual Fatalities (faceted by State)

```{r}
p <- ggplot(df_total, aes(x = Year, y = Fatalities)) + geom_col() + 
  facet_wrap("State", nrow = 1)
ggplotly(p)
```

### Annual Fatalities (faceted by State)

```{r}
p <- ggplot(df_total, aes(x = Year, y = Fatalities)) + geom_point() + 
  geom_smooth(formula = y ~ x, method = "lm") + 
  facet_wrap("State", nrow = 1)
ggplotly(p)
```

Row {data-height=300}
-----------------------------------------------------------------------

```{r}
df_category <- df %>% 
  filter(!is.na(Char_1), !is.na(Char_2),  is.na(Char_3)) %>% 
  mutate(Year = factor(Year)) %>%
  filter(Char_1 != "Total") %>% 
  group_by(Char_1, Year, State) %>% 
  summarize(Fatalities = sum(Fatalities, na.rm = TRUE), .groups= "drop") %>%
  arrange(Char_1, State, Year, Fatalities)
```

### Annual Fatalities (faceted by Category)

```{r}
p <- ggplot(df_category, aes(x = Year, y = Fatalities, fill = State)) + 
  geom_col() + facet_wrap("Char_1", nrow = 2) + 
  theme(axis.text.x = element_text(angle = 90))
ggplotly(p)
```

```{r}
pers_char <- c("Gender", "Employee status", "Age", "Race or ethnic origin")
df_personal_char2 <- df %>% 
    mutate(Year = factor(Year)) %>%
    filter(!is.na(Char_1), !is.na(Char_2), is.na(Char_3), 
           Char_1 %in% pers_char) %>% 
    rename("Category" = Char_1) %>%
    group_by(Category, Characteristic) %>% 
    summarise(Fatalities = sum(Fatalities, na.rm = TRUE), .groups = "drop") %>% 
    arrange(desc(Fatalities), Category, Characteristic) %>% 
    select(Fatalities, Category, Characteristic)
p <- map(pers_char, ~ ggplot(df_personal_char2 %>% filter(Category == .x), 
            aes(x  = fct_reorder(Characteristic, Fatalities), 
                y = Fatalities)) + 
  geom_col() + coord_flip() + xlab("Characteristic")) %>% setNames(pers_char)
```

Row {data-height=200}
-----------------------------------------------------------------------

### Total Fatalities, by Employee status

```{r}
ggplotly(p[['Employee status']])
```

### Total Fatalities, by Gender

```{r}
ggplotly(p[['Gender']])
```

Row {data-height=400}
-----------------------------------------------------------------------

### Total Fatalities, by Age

```{r}
ggplotly(p[['Age']])
```

### Total Fatalities, by Race or ethnic origin

```{r}
ggplotly(p[['Race or ethnic origin']])
```

Row {data-height=600}
-----------------------------------------------------------------------

### Total Fatalities, Top-15 Characteristics (excluding employee status or personal characteristics)

```{r}
df_top15_char3 <- df %>% 
    mutate(Year = factor(Year)) %>%
    filter(!is.na(Char_1), !is.na(Char_2), !is.na(Char_3), is.na(Char_4), 
           ! Char_1 %in% c("Total", "Gender", "Employee status", "Age",
                           "Race or ethnic origin")) %>% 
    mutate(Characteristic = str_wrap(paste(Char_1, Char_2, Char_3, sep = ": "), 60)) %>%
    group_by(Char_1, Characteristic) %>% 
    summarise(Fatalities = sum(Fatalities, na.rm = TRUE), .groups = "drop") %>% 
    arrange(desc(Fatalities), Char_1, Characteristic) %>% 
    select(Fatalities, Category = Char_1, Characteristic) %>% head(15)
p <- ggplot(df_top15_char3, 
            aes(x  = fct_reorder(Characteristic, Fatalities), 
                y = Fatalities,
                fill = Category)) + 
  geom_col() + coord_flip() + 
  xlab("Characteristic")
ggplotly(p)
```


Row {data-height=1200}
-----------------------------------------------------------------------

### Annual Fatalities, Top-15 Characteristics (excluding employee status or personal characteristics)

```{r}
df_top15 <- df %>% 
  mutate(Year = factor(Year)) %>%
  filter(!is.na(Char_1), !is.na(Char_2), !is.na(Char_3), is.na(Char_4), 
         ! Char_1 %in% c("Total", "Gender", "Employee status", "Age",
                         "Race or ethnic origin")) %>% 
  mutate(Characteristic = str_wrap(paste(Char_1, Char_2, Char_3, sep = ": "), 60)) %>%
  filter(Characteristic %in% df_top15_char3$Characteristic) %>%
  group_by(Characteristic, Year, State) %>% 
  summarise(Fatalities = sum(Fatalities, na.rm = TRUE), .groups = "drop") %>% 
  arrange(desc(Fatalities), Year, State, Characteristic)
p <- ggplot(df_top15, aes(x = Year, y = Fatalities, fill = State)) + 
  geom_col() + facet_wrap("Characteristic", ncol = 3) + 
  theme(axis.text.x = element_text(angle = 90))
ggplotly(p)
```

Employee status
=======================================================================

Row {data-height=300}
-----------------------------------------------------------------------

### Employee status: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_scatterplot(df, "Employee status", by = "State"))
```

Row {data-height=300}
-----------------------------------------------------------------------

### Employee status: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_scatterplot(df, "Employee status", by = "Year"))
```


Gender
=======================================================================

Row {data-height=300}
-----------------------------------------------------------------------

### Gender: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_scatterplot(df, "Gender", by = "State"))
```

Row {data-height=300}
-----------------------------------------------------------------------

### Gender: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_scatterplot(df, "Gender", by = "Year"))
```


Age
=======================================================================

Row {data-height=550}
-----------------------------------------------------------------------

### Age: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_barplot(df, "Age", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Age: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_barplot(df, "Age", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Age: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Age", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Age: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Age", by = "Year"))
```


Race or ethnic origin
=======================================================================

Row {data-height=550}
-----------------------------------------------------------------------

### Race or ethnic origin: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_barplot(df, "Race or ethnic origin", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Race or ethnic origin: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_barplot(df, "Race or ethnic origin", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Race or ethnic origin: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Race or ethnic origin", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Race or ethnic origin: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Race or ethnic origin", by = "Year"))
```


Event or exposure
=======================================================================

Row {data-height=550}
-----------------------------------------------------------------------

### Event or exposure: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_barplot(df, "Event or exposure", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Event or exposure: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_barplot(df, "Event or exposure", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Event or exposure: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Event or exposure", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Event or exposure: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Event or exposure", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Transportation incidents: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Event or exposure", "Transportation incidents", 
                      by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Transportation incidents: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Event or exposure", "Transportation incidents", 
                      by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Transportation incidents: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_scatterplot(df, "Event or exposure", "Transportation incidents", 
                          by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Roadway incidents involving motorized land vehicle: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Event or exposure", "Transportation incidents", 
                      "Roadway incidents involving motorized land vehicle", 
                      by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Roadway incidents involving motorized land vehicle: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Event or exposure", "Transportation incidents", 
                      "Roadway incidents involving motorized land vehicle", 
                      by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Roadway incidents involving motorized land vehicle: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_scatterplot(df, "Event or exposure", "Transportation incidents", 
                          "Roadway incidents involving motorized land vehicle", 
                          by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Contact with objects and equipment: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Event or exposure", 
                      "Contact with objects and equipment", 
                      by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Contact with objects and equipment: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Event or exposure", 
                      "Contact with objects and equipment", 
                      by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Contact with objects and equipment: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_scatterplot(df, "Event or exposure", 
                          "Contact with objects and equipment", 
                          by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Contact with objects and equipment: Struck by object or equipment: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Event or exposure", 
                      "Contact with objects and equipment", 
                      "Struck by object or equipment",
                      by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Contact with objects and equipment: Struck by object or equipment: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Event or exposure", 
                      "Contact with objects and equipment", 
                      "Struck by object or equipment", 
                      by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Contact with objects and equipment: Struck by object or equipment: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_scatterplot(df, "Event or exposure", 
                          "Contact with objects and equipment", 
                          "Struck by object or equipment",
                          by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Event or exposure: Top-3 Subcategory Characteristics: Annual Fatalities (faceted by Characteristic)

```{r}
p <- plot_bar_char(df, top3[['Event or exposure']]) + 
  theme(axis.text.x = element_text(angle = 90))
ggplotly(p)
```


Nature
=======================================================================

Row {data-height=550}
-----------------------------------------------------------------------

### Nature: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_barplot(df, "Nature", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Nature: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_barplot(df, "Nature", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Nature: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Nature", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Nature: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Nature", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Other traumatic injuries and disorders: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Nature", "Other traumatic injuries and disorders", 
                      by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Other traumatic injuries and disorders: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Nature", "Other traumatic injuries and disorders", 
                      by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Nature: Top-3 Subcategory Characteristics: Annual Fatalities (faceted by Characteristic)

```{r}
p <- plot_bar_char(df, top3[['Nature']]) + 
  theme(axis.text.x = element_text(angle = 90))
ggplotly(p)
```


Primary source
=======================================================================

Row {data-height=550}
-----------------------------------------------------------------------

### Primary source: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_barplot(df, "Primary source", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Primary source: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_barplot(df, "Primary source", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Primary source: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Primary source", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Primary source: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Primary source", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Vehicles: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Primary source", "Vehicles", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Vehicles: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Primary source", "Vehicles", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Vehicles: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_scatterplot(df, "Primary source", "Vehicles", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Vehicles: Highway vehicles, motorized: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Primary source", "Vehicles", 
                      "Highway vehicles, motorized", 
                      by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Vehicles: Highway vehicles, motorized: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Primary source", "Vehicles", 
                      "Highway vehicles, motorized", 
                      by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Vehicles: Highway vehicles, motorized: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_scatterplot(df, "Primary source", "Vehicles", 
                          "Highway vehicles, motorized", 
                          by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Persons, plants, animals, and minerals: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Primary source", 
                      "Persons, plants, animals, and minerals", 
                      by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Persons, plants, animals, and minerals: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Primary source", 
                      "Persons, plants, animals, and minerals", 
                      by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Persons, plants, animals, and minerals: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_scatterplot(df, "Primary source", 
                          "Persons, plants, animals, and minerals", 
                          by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Primary source: Top-3 Subcategory Characteristics: Annual Fatalities (faceted by Characteristic)

```{r}
p <- plot_bar_char(df, top3[['Primary source']]) + 
  theme(axis.text.x = element_text(angle = 90))
ggplotly(p)
```


Secondary source
=======================================================================

Row {data-height=550}
-----------------------------------------------------------------------

### Secondary source: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_barplot(df, "Secondary source", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Secondary source: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_barplot(df, "Secondary source", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Secondary source: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Secondary source", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Secondary source: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Secondary source", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Secondary source: Top-3 Subcategory Characteristics: Annual Fatalities (faceted by Characteristic)

```{r}
p <- plot_bar_char(df, top3[['Secondary source']]) + 
  theme(axis.text.x = element_text(angle = 90))
ggplotly(p)
```


Worker activity
=======================================================================

Row {data-height=550}
-----------------------------------------------------------------------

### Worker activity: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_barplot(df, "Worker activity", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Worker activity: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_barplot(df, "Worker activity", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Worker activity: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Worker activity", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Worker activity: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Worker activity", by = "Year"))
```


Part of body
=======================================================================

Row {data-height=550}
-----------------------------------------------------------------------

### Part of body: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_barplot(df, "Part of body", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Part of body: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_barplot(df, "Part of body", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Part of body: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Part of body", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Part of body: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Part of body", by = "Year"))
```


Row {data-height=550}
-----------------------------------------------------------------------

### Part of body: Top-3 Subcategory Characteristics: Annual Fatalities (faceted by Characteristic)

```{r}
p <- plot_bar_char(df, top3[['Part of body']]) + 
  theme(axis.text.x = element_text(angle = 90))
ggplotly(p)
```


Location
=======================================================================

Row {data-height=550}
-----------------------------------------------------------------------

### Location: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_barplot(df, "Location", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Location: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_barplot(df, "Location", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Location: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Location", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Location: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Location", by = "Year"))
```


Occupation
=======================================================================

Row {data-height=550}
-----------------------------------------------------------------------

### Occupation: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_barplot(df, "Occupation", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Occupation: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_barplot(df, "Occupation", by = "Year"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Occupation: Annual Fatalities (faceted by State)

```{r}
ggplotly(make_boxplot(df, "Occupation", by = "State"))
```

Row {data-height=550}
-----------------------------------------------------------------------

### Occupation: Fatalities per State (faceted by Year)

```{r}
ggplotly(make_boxplot(df, "Occupation", by = "Year"))
```

